Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-04-30 journal-draft/ettdoc.tex
Modify the expressions pointed by Erwin

\section{Introduction}
\label{intro}
%CR concept
Cognitive radio (CR) is a promising technology to solve the spectrum scarcity problem for the upcomging era of internet of things~\cite{Mitola, Rawat20161}.
Licensed users access the spectrum allocated to them whenever there is information to be transmitted.
In contrast, as one way, unlicensed users can access the spectrum via opportunistic spectrum access, \ie they access the licensed spectrum only after validating the channel is unoccupied by licensed users, where spectrum sensing~\cite{sensing_survey_2009} plays an important role in this process.
%
In this hierarchical spectrum access model~\cite{zhao_survey_DSA_2007}, the licensed users are also called primary users (PU), while the unlicensed users are referred to as secondary users and constitute a so called cognitive radio network (CRN).
%
%cluster
Regarding the operation of CRN, efficient spectrum sensing is identified to be critical for a smooth operation of a cognitive radio network~\cite{Sahai_FundamentalDesignTradeoffs2006}.
Efficient spectrum sensing can be achieved by cooperative spectrum sensing of multiple secondary users, which has been shown to cope effectively with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
Collaborative sensing relies on the consensus of CR users\footnote{The terms user and node appear interchangeably in this paper. In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer to nodes typicallly in the context of the network topology.} within a certain area, in this regard, clustering is regarded as an effective method to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing}.
% ... decreases considerably the negative probability due to the random channel effects like fading and shadowing.
Clustering is a process of grouping certain users in geographic proximity into a collective.
In the context of cognitive radio netowrks, a formed cluster helps the participants not only to improve the spectrum sensing accuracy, but also to coordinate the channel switch operation when the primary users are detected by at least one secondary user in that cluster. Then all the cluster menmbers can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
Clustering also benefits the operation of a CRN by reducing the interference between cognitive clusters~\cite{centralizedSharing80222}, and supporting routing~\cite{Abbasi_survey_07}.
%As to the coexistence of CR users, they can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}. 
Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects, which has already been discussed in many works. [CITATION MISSING]

@@

The drawbacks of this scheme are as follows, although the adopted metric considers both cluster size and the number of CCs, cluster formation can be easily dominated by only one factor, e.g. a node which can access many channels may exclude its neighbor and form a cluster by itself. (THIS SENTENCE IS TOO COMPLICATED. BREAK IT DOWN TO 2 OR 3 PLEASE.)

@@

First, this paper renews the definition of robustness of clusters in a CRN, which is no longer the average number of CCs of clusters, but the ability of the clusters to sustain when the primary users' activity becomes more dynamic. (BAD FORMULATION TO SAY "renew". Changing definitions itself does not impose any benefit. Is there any an improval?)
Second, this paper proposes size control mechanism, which solves the problem of devergence of clusters sizes in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
Besides, this paper provides a comprehensive analysis of the robust clustering problem and proposes a centralized solution. 

>>>>

\section{Introduction}
\label{intro}
%CR concept
Cognitive radio (CR) is a promising technology to solve the spectrum scarcity problem for the upcomging era of internet of things~\cite{Mitola, Rawat20161}.
Licensed users access the spectrum allocated to them whenever there is information to be transmitted.
In contrast, as one way, unlicensed users can access the spectrum via opportunistic spectrum access, \ie they access the licensed spectrum only after validating the channel is unoccupied by licensed users, where spectrum sensing~\cite{sensing_survey_2009} plays an important role in this process.
%
In this hierarchical spectrum access model~\cite{zhao_survey_DSA_2007}, the licensed users are also called primary users (PU), while the unlicensed users are referred to as secondary users and constitute a so called cognitive radio network (CRN).
%
%cluster
Regarding the operation of CRN, efficient spectrum sensing is identified to be critical for a smooth operation of a cognitive radio network~\cite{Sahai_FundamentalDesignTradeoffs2006}.
Efficient spectrum sensing can be achieved by cooperative spectrum sensing of multiple secondary users, which has been shown to cope effectively with noise uncertainty and channel fading, thus remarkably improving the sensing accuracy~\cite{coorperativeSensing_Akyildiz11}.
Collaborative sensing relies on the consensus of CR users\footnote{The terms user and node appear interchangeably in this paper. In particular, user is adopted when its networking or cognitive ability are discussed or stressed, while we refer to nodes typicallly in the context of the network topology.} within a certain area, in this regard, clustering is regarded as an effective method to realize cooperative spectrum sensing~\cite{Sun07_clustering_spectrum_secsing}.
% ... decreases considerably the negative probability due to the random channel effects like fading and shadowing.
Clustering is a process of grouping certain users in geographic proximity into a collective.
In the context of cognitive radio netowrks, a formed cluster helps the participants not only to improve the spectrum sensing accuracy, but also to coordinate the channel switch operation when the primary users are detected by at least one secondary user in that cluster. Then all the cluster menmbers can stop payload transmission swiftly and vacate the operating channel ~\cite{willkomm08}.
Clustering also benefits the operation of a CRN by reducing the interference between cognitive clusters~\cite{centralizedSharing80222}, and supporting routing~\cite{Abbasi_survey_07}.
%As to the coexistence of CR users, they can be notified by cluster head (CH) or other cluster members about the possible collision, the possibility for them to interfere neighbouring clusters is reduced~\cite{centralizedSharing80222}. 
Except for benefiting the dynamic spectrum sharing in CRN, clustering contributes to the other wireless networks in many aspects, which has already been discussed in many works~\cite{Kawadia03, clustering_mesh_globecom2010, Abbasi_survey_07}.

@@

The drawbacks of this scheme are as follows, although the adopted metric considers both the cluster size and the number of CCs, cluster formation can be easily dominated by only one factor.
For example, a node which accesses abundant channels may form a cluster by itself and doesn't have motivation to unite neighboring nodes to form a cluster.

@@

First, this paper considers the correlation between the cluster robustness and the cluster size.
As a result the cluster robustness is no longer indicated merely by the average number of CCs of clusters, but the ability of the CR nodes to get benefit from collective decision and of the clusters to sustain when the primary users' activity becomes more dynamic.
Besides, this involment of cluster size enable us to solve the problem of clusters size devergence, which appears in~\cite{Li11_ROSS} and~\cite{LIU_TMC11_2}.
Second, this paper provides a comprehensive analysis of the robust clustering problem, proposes both centralized and distributed solutions, and conducts extensive simulations. 
